\documentclass{../codeproblem}

\begin{document}

\title{Querying Khan}


\begin{flavor}
  When Seymore Time Traveler has problems, he doesn't fret! He has
  friends all across the timeline to help him out!
\end{flavor}

\section*{Description}

After visiting many of his friends across time, our favorite time
traveler arrived at the dwelling of one Genghis Khan. After a night
filled with tom-foolery and shenanigans, Seymore asked his friend for
some help:
\begin{flavor}
  Ok, Genghis, here is my problem. I have the \emph{DISTANCE} between
  multiple points, but I don't actually know their location! Can you
  help me make a map of where the points must be?!
\end{flavor}
To which Genghis responded by killing thousands.

\section*{Example Input/Output}
Each line of input will include a pair of labels, and their
``Manhattan distance'' between each other. You must print out a 10x10
table, using the \texttt{*} to represent empty space, and a letter to
represent the valid points.

\begin{minipage}{.5\linewidth}
  \begin{example}
|\textbf{input:}|
A B 5
A C 9
B C 5
|\textbf{output:}|
A*********
**********
**********
**********
B***C*****
**********
**********
**********
**********
**********
**********



|\end{example}
\end{minipage}
\begin{minipage}{.5\linewidth}
\begin{example}
|\textbf{input:}|
A B 10 
A C 6
A D 6
B C 5
B D 9
C D 5
|\textbf{output:}|
**********
**********
*******A**
**********
B***C*****
**********
******D***
**********
**********
**********
**********
|\end{example}
\end{minipage}



\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
