\documentclass{../codeproblem}

\begin{document}

\title{Chutes and SPACE-LADDERS}

\begin{flavor}
  While exploring the future, Seymore Time Traveler discovered a new
  technology --- the LASER-AIDED-DIMENSIONAL-DRIFT-ENERGY-RIDER!
\end{flavor}

\section*{Description}
Our hero is, yet again, in a predicament of laziness. He has discovered
many exciting new worlds, connected together by \emph{SPACE WORMHOLES}! He
would love to travel through them\ldots but he doesn't want to travel
through \emph{too} many wormholes (because that sounds hard).

Your task, should you choose to accept it, is to find the shortest
path from the starting world to the destination of Seymore's choice.

\section*{Example Input/Output}

Each of the first $n$ lines of input will be a world name (a single
upper-case character), followed by a list of each connected world. 
. The $n+1$'th line will be a single upper-case
letter, designating the desired destination. You must output a
sequence of letters that represents the shortest path to the
destination. Assume you start at the first given world. You can assume
a path will always exist. There will be less than 10 worlds given.
If multiple valid paths exist, any will be accepted.


\begin{minipage}{.33\linewidth}
  \begin{example}
|\textbf{input:}|
A B D
B C D
C
|\textbf{output:}|
A B C


|\end{example}
\end{minipage}
\begin{minipage}{.33\linewidth}
\begin{example}
|\textbf{input:}|
A B D
B C D
A
|\textbf{output:}|
A


|\end{example}
\end{minipage}
\begin{minipage}{.33\linewidth}
\begin{example}
|\textbf{input:}|
A B C D
B F
D B C
F E
E
|\textbf{output:}|
A B F E|\end{example}
\end{minipage}

\end{document}
