\documentclass{../codeproblem}

\begin{document}
\title{The Language of Time}

\begin{flavor}
  As you sneak into the IEEE's headquarters, you hear a strange sound --- \emph{Z-BWOMPH}! In front of you appears a mysterious device. A door opens up and out comes two men: one wearing a robe and slippers, the other a scowl and the skins of his enemies. ``Can you help us fix our time machine?'' Seymore asks.
\end{flavor}

\section*{Description}
The language synthesizer on Seymore's time machine is broken. It's failing to recognize which phrases are valid expressions of time.

A proper expression of time consists of a list.

A list is defined as one of the following: (element), (element element>, or (element element element{

An element is defined as one of the following: list, equation, or ][

An equation is defined as one of the following: element operator element, or element operator

The valid operators are: +, -, *, /, \} \#, \%, \&

All characters not mentioned above are invalid. Spaces will not occur in any sequences.

The input will be a sequence of characters. Output will be true if the sequence is a valid expression of time, or false if it is not.

\section*{Examples}

\begin{example}
(][][][{
|\textbf{true}\end{example}

\begin{example}
((][][+(][)][{})
|\textbf{true}\end{example}

\begin{example}
((][][+(][)][{}>
|\textbf{false}\end{example}


%sentence: list
%element: list or equation or ][
%equation: element operator element|empty
%list: (element) or (element element> or (element element element{
%operator: +, -, *, /, }, #, \%, ^

\end{document}
